Lattice model

### 2017-04-10 oopsla17/lattice-model.tex
Fix distance definition for the origin
Fix the connecting lemma

  This notion extends to subscripts. Since there may be an infinite number of
  points, we measure the distance from the closest one.
\end{defn}
%
\begin{prop}{}
  The closed form of extend origin distance for an $N$-dimensional subscript $S$
  is denoted with $\mathit{dist}(S)$ and is defined as:
%
  \begin{align*}
    \mathit{dist}(S) & = \sum_{i=1}^{N} \mathit{dist}_i(S)
    &
    \mathit{dist}_i(S) & = \begin{cases}
      0 & \pi_i(S) = \interv{-\infty}{\infty}{} \\
      |\mathsf{a}| - 1 & \pi_i(S) = \{\mathsf{a}\} \\
    \end{cases}
  \end{align*}
\end{prop}
%
\begin{proof}
  Now we prove that function $\mathit{dist}$ indeed gives the lowest number of
  unit translations to reach the extended origin.
\end{proof}

@@

\begin{lem}{(\emph{Connecting})}
  The following three statements are equivalent for a set of points $P \subseteq
  \mathbb{Z}^N$:
%
  \begin{enumerate}
    \item $P$ is the same as its exact set $\mathit{ES}_P$;
    \item $P$ when regarded as offsets from induction variables forms a
      neighbourhood stencil;
    \item $P$ is a subset of \region{N}.
  \end{enumerate}
\end{lem}

>>>>

  This notion extends to subscripts. Since there may be an infinite number of
  points, we measure the distance from the closest one.
\end{defn}
%
\begin{prop}{}
  The closed form of extend origin distance for an $N$-dimensional subscript $S$
  is denoted with $\mathit{dist}(S)$ and is defined as:
%
  \begin{align*}
    \mathit{dist}(S) & = \sum_{i=1}^{N} \mathit{dist}_i(S)
    &
    \mathit{dist}_i(S) & = \begin{cases}
      0 & \pi_i(S) \in \{ \interv{-\infty}{\infty}{}, \{ 0 \}\} \\
      |\mathsf{a}| - 1 & \pi_i(S) = \{\mathsf{a}\} \\
    \end{cases}
  \end{align*}
\end{prop}
%
\begin{proof}
  Now we prove that function $\mathit{dist}$ indeed gives the lowest number of
  unit translations to reach the extended origin.
\end{proof}

@@

\begin{lem}{(\emph{Connecting})}
  The following three statements are equivalent for a set of $N$-dimensional
  subscripts $S$:
%
  \begin{enumerate}
    \item $S$ is the same as its exact set $\mathit{ES}_S$;
    \item $S$ when regarded as offsets from induction variables forms a
      neighbourhood stencil;
    \item $S$ is in \region{N}.
  \end{enumerate}
\end{lem}
